Summary Tables

### 2020-03-02 summary_tables.Rmd
Fix title
Change heading number
Add row sums for average and total distance, and trip prop

@@

@@

## Baseline total distance tables for all case studies (per year in km)

@@

td <- as.data.frame(bl_td)

>>>>

trip_prop <- trip_prop %>% dplyr::filter(stage_mode != "row_sums") %>% mutate_if(is.factor, ~ as.numeric(as.character(.x))) %>% janitor::adorn_totals('row')

@@

trip_dist <- trip_dist %>% janitor::adorn_totals('row')

@@

### Baseline total distance for all case studies (per year in km)

@@

td <- as.data.frame(bl_td) %>% janitor::adorn_totals('row')
